\documentclass{article}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\usepackage[margin=60pt]{geometry}
\usepackage{hyperref}
\usepackage{makeidx}
\usepackage{graphicx}
\graphicspath{{./res/}}
\makeindex
\begin{document}
\begin{titlepage}
   \vspace*{\stretch{1.0}}
   \begin{center}
      \Huge\textbf{Home Challenge \#1: Sniffing}\\
      \vspace{5mm} %5mm vertical space
      \Large Prof. Matteo Cesana - Year 2020/2021\\
      \vspace{5mm} %5mm vertical space
      \large\textit{Name Surname [codice persona: X]}
      \linebreak
      \large\textit{Tortorelli Giuseppe [codice persona: 10582962]}
   \end{center}
   \vspace*{\stretch{2.0}}
\end{titlepage}
\printindex

\tableofcontents
\pagebreak


\section{What’s the difference between the message with MID:
3978 and the one with MID: 22636?}
\section{Does the client receive the response of message No.
6949?}
\section{How many replies of type confirmable and result code
“Content” are received by the server “localhost”?}
\section{How many messages containing the topic
“factory/department*/+” are published by a client with
user name: “jane”? Where * replaces the dep. number,
e.g. factory/department1/+, factory/department2/+
and so on?}
\section{How many clients connected to the broker “hivemq”
have specified a will message?}
\section{How many publishes with QoS 1 don’t receive the ACK?}
\section{How many last will messages with QoS set to 0 are
actually delivered?}
\section{Are all the messages with QoS > 0 published by the
client “4m3DWYzWr40pce6OaBQAfk” correctly delivered
to the subscribers?}
\section{What is the average message length of a connect msg
using mqttv5 protocol? Why messages have different
size?}
\section{Why there aren’t any REQ/RESP pings in the pcap?}

\end{document}